Model to study co-evolution of trade an culture

### 2015-04-02 article.tex
multicol

\begin{table}[h]
	\centering
	\begin{tabular}{ll|lllll}
		Agents Number & & Our result& & Bentley et al 2004\\
			&$\mu$ & $\alpha$ & SD&$\alpha$&SD\\\hline

		N = 250 
			&0.004&1.53&0.03&1.54&0.02\\
			&0.008&1.55&0.03&1.55&0.01\\
			&0.016&1.57&0.02&1.57&0.01\\
			&0.064&1.66&0.01&1.67&0.01\\\hline
		N= 500
		&0.004&1.50&0.02&1.53&0.03\\
		&0.008&1.52&0.02&1.57&0.01\\
		&0.016&1.55&0.03&1.61&0.04\\
		&0.064&1.78&0.08&1.81&0.10\\
	\end{tabular}
	\caption{Mean \& SD are calculate on 100 run.}
	\label{tab:mualpha}
\end{table}

>>>>

\begin{table}[h]
	\centering
	\begin{tabular}{ll|llll}
		\multicolumn{2}{r}{Agents Number}&\multicolumn{2}{c}{Our result}&\multicolumn{2}{c}{Bentley et al 2004}\\
			&$\mu$ & $\alpha$ & SD&$\alpha$&SD\\\hline
		N = 250	&0.004&1.53&0.03&1.54&0.02\\
			&0.008&1.55&0.03&1.55&0.01\\
			&0.016&1.57&0.02&1.57&0.01\\
			&0.064&1.66&0.01&1.67&0.01\\\hline
		N= 500	&0.004&1.50&0.02&1.53&0.03\\
			&0.008&1.52&0.02&1.57&0.01\\
			&0.016&1.55&0.03&1.61&0.04\\
			&0.064&1.78&0.08&1.81&0.10\\
	\end{tabular}
	\caption{Mean \& SD are calculate on 100 run.}
	\label{tab:mualpha}
\end{table}
